---
output: github_document
---

<!-- <style>body {max-width: 1100px; margin: auto; padding: 1em; line-height: 20px ;}</style>-->

  <!-- README.md is generated from README.Rmd. Please edit that file -->


<!-- -->
<!-- FILL OUT OPTIONS !!! -->
<!-- -->
```{r scaffolding options, include=FALSE}
github_user_name   <- "petermeissner"
codecov_user_name  <- github_user_name
travis_user_name   <- github_user_name
appveyor_user_name <- github_user_name
```
<!-- -->
<!-- -->




```{r knitr options, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/README-"
)
```


```{r r options, include=FALSE}
options("width" = 110)
options(scipen = 20)

# get package info
tmp <- packageDescription( "kafkaesque" )

package_name <- tmp$Package

```

```{r readme title, results='asis', echo=FALSE}
cat("#", tmp$Title)
```

```{r, include=FALSE}
md_list <- 
  function(x, item_string = c("-", "*", "+"), item_ident = c("", "  ", "    ")){
    
    for ( i in seq_along(x)){
      
      cat(item_ident[1], item_string[1], " **", names(x)[[i]], "**\n", sep = "")
      
      if ( is.list(x[[i]]) & !is.null(names(x[[i]])) ){
        
        lapply(x[[i]], md_list, item_string = item_string[-1], item_ident = item_ident[-1])
        
      } else {
        
        for (k in seq_along(x[[i]])) {
          cat(item_ident[-1][1], item_string[-1][1], " ", x[[i]][[k]], "\n", sep = "")
        }
        
      }
    }  
  }

```



**Status**

[![codecov](https://codecov.io/gh/petermeissner/kafkaesque/branch/master/graph/badge.svg?token=jzamre15u6)](https://codecov.io/gh/petermeissner/kafkaesque)<!--<img src="http://www.r-pkg.org/badges/version/`r package_name`"><img src="http://cranlogs.r-pkg.org/badges/grand-total/`r package_name`"><img src="http://cranlogs.r-pkg.org/badges/`r package_name`">-->[![Check, Test, Lint](https://github.com/petermeissner/kafkaesque/actions/workflows/tests.yml/badge.svg)](https://github.com/petermeissner/kafkaesque/actions/workflows/tests.yml)


This package is - so far - feature complete and should be functional. 
This is a structured extract and rewrite from client work.
Though core parts of the package are used in production and are 'battle tested'
the package presented here is not - so far.


Package has not been published to CRAN. 
Attempts have been made. 
CRAN has a policy on package size (<= 5MB) and publishing to CRAN would mean only 
publishing the R code without any Java dependencies.
One can add an install function that downloads the necessary JAR files 
after installing the package from CRAN.
So far no decision has been made if I should pursue this way or not. 





```{r, include=FALSE}
filelist.R     <- list.files("R", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.Java  <- list.files("java/kafkaesque/src/main/java/kafkaesque", recursive = TRUE, pattern="\\.java$", ignore.case = TRUE, full.names = TRUE)
filelist.tests   <- list.files("tests", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.cpp <- list.files("src", recursive = TRUE, pattern="\\.cpp$", ignore.case = TRUE, full.names = TRUE)
lines.R      <- unlist(lapply(filelist.R, readLines))
lines.Java   <- unlist(lapply(filelist.Java, readLines, warn=FALSE))
lines.tests  <- unlist(lapply(filelist.tests, readLines))
lines.cpp    <- unlist(lapply(filelist.cpp, readLines))
length.R     <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.R,  value = TRUE, invert = TRUE))
length.Java  <- length(grep("(^\\s*$)|(^\\s*/*\\*)|(^\\s*#)|(^\\s*//)", lines.Java,  value = TRUE, invert = TRUE))
length.tests <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.tests,  value = TRUE, invert = TRUE))
length.cpp   <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.cpp,  value = TRUE, invert = TRUE))
```


*lines of R code:* `r length.R`, *lines of Java code:* `r length.Java`, *lines of test code:* `r length.tests`



**Version**

```{r, include=FALSE}
source_files <-
  grep(
    "/R/|/src/|/tests/",
    list.files(recursive = TRUE, full.names = TRUE),
    value = TRUE
  )
last_change <-
  as.character(
    format(max(file.info(source_files)$mtime), tz="UTC")
  )
```


```{r, results='asis', echo=FALSE}
cat(tmp$Version, "(",last_change,")")
```

**Description**


```{r, results='asis', echo=FALSE}
cat(tmp$Description)
```


**License**

```{r, results='asis', echo=FALSE}
cat(tmp$License, "<br>")
cat(tmp$Author)
```



**Citation**


```{r, results='asis', echo=FALSE}
cat("```r\n")
cat("citation(\"",package_name,"\")", sep = "")
cat("\n```\n")
```

```{r, results='asis', echo=FALSE}
cat("```r\n")
print_text <- capture.output(print(citation(package_name), style = "text"))
cat(gsub("_", "", print_text))
cat("\n```\n")
```


**BibTex for citing**

```{r, results='asis', echo=FALSE}
cat("```r\n")
cat("toBibtex(citation(\"",package_name,"\"))", sep = "")
cat("\n```\n")
```

```{r, results='asis', echo=FALSE}
cat("```\n")
cat(as.character(toBibtex(citation(package_name))), sep = "\n")
cat("\n```\n")
```



**Installation**

<!-- Stable version from CRAN: -->




<!-- ```{r, results='asis', echo=FALSE} -->
<!-- cat("```r\n") -->
<!-- cat("install.packages(\"",package_name,"\")", sep = "") -->
<!-- cat("\n```\n") -->
<!-- ``` -->


Latest development version from Github:


```{r, results='asis', echo=FALSE}
cat("```r\n")
cat("devtools::install_github(\"petermeissner/",package_name,"\")", sep = "")
cat("\n```\n")
```

<!-- # ToDos -->

<!-- ```{r, results='asis'} -->
<!-- md_list(kafkaesque:::todo) -->
<!-- ``` -->



# Content 

```{r}
library(kafkaesque)
ls("package:kafkaesque")
```

# Usage


## Consumer

### Start Consumer (... Stop, Status)

```{r}

library("kafkaesque")

# new consumer
consumer <- kafka_consumer()

# starting/connecting - + status
consumer$start()

consumer$running()
consumer$end()$running()
consumer$start()$running()

```



### Properties aka Config

See here for list of consumer properties: https://kafka.apache.org/documentation/#consumerconfigs.


```{r}
consumer$props()
```


```{r}
consumer$props(max.poll.records = 200)
```



### Topics and Subscriptions

```{r}

# list topics available to consumer
consumer$topics_list()

# subscribe to topic
consumer$topics_subscribe("test500000")
consumer$topics_subscription()


```



### Retrieving a Message

```{r}

# retrieve next message
consumer$consume_next()

```


### Looping over Messages and Executing Code


```{r}
# loop over messages and execute code
res <- 
  consumer$consume_loop(
    f     = function(loop_env){ print(loop_env$messages)},
    check = function(loop_env){loop_env$meta$loop_counter < 4},
    batch = TRUE
  )

# having a look at the statistics
res


```

### Looping over Batches of Messages and Executing Code

```{r}

# loop over batches of messages and execute code
res <- 
  consumer$consume_loop(
    f     = function(loop_env){ print(loop_env$messages); cat("\n")},
    check = function(loop_env){loop_env$meta$message_counter < 1000},
    batch = TRUE
  )

res

```


### Offsets and Seeking


```{r}
# get current offsets from Kafka
consumer$topics_offsets()

# seek to end of topics 
consumer$topics_seek_to_end()
consumer$topics_offsets()

# seek to beginning of topics
consumer$topics_seek_to_beginning()
consumer$topics_offsets()

```



## Producer


### Start Producer (... Stop, Status)

```{r}

library("kafkaesque")

# new producer
producer <- kafka_producer()

# starting/connecting - + status
producer$start()

producer$running()
producer$end()$running()
producer$start()$running()
producer$restart()$running()

```


### Properties aka Config

See here for list of consumer properties: https://kafka.apache.org/documentation/#producerconfigs.


```{r}
producer$props()
```


```{r}
producer$props(whatever.you.may.want.to.set = "true")
```



### Sending Messages

```{r}
producer$send(topic = "test", msg = "Die Kuh macht muh.")
producer$send(topic = "test", msg = "Das Schaf macht mäh.")
producer$send(topic = "test", msg = "Das Pferd macht wihiiiiiiiii-pffffff.")
```




## Setting and Getting Java-LogLEvels


```{r}
kafka_get_log_level()

# one of off, fatal, error, warn, info, debug, trace, all
kafka_set_log_level("info")
producer$start()


# set back to normal
kafka_set_log_level("error")
```




## Admin

### Properties aka Config


```{r}
admin <- kafka_admin()
admin$start()

admin$props()
admin$props(whatever.you.may.want.to.set = "true")
```


### Get List of Topics 

```{r}
admin$topics_list()
```



### Create Topics

```{r}
admin$topics_list()

topics <- c("chuckle", "chit_chat")
admin$topics_create(
  topic              = topics, 
  partition         = c(1L, 1L), 
  replication_factor = c(1L, 1L)
)
```



### Delete Topics 



```{r}
admin$topics_delete(topics)
```







# Developement Notes

For R development Rstudio was used. For Java development Visual Studio Code
lend a helping hand with Maven as build tooling. 

For development one packages is needed:

- {kafkaesque} contains all the R functions, classes and methods and also all 
Java code that is specific to this project (and not just a dependency)

Java sources are in `./java/kafkaesque/` folder - so your Java project should 
take this as root folder. 
Building Java sources can be 
done via Maven: `mvn install` will compile everything and copy the `kafkaesque.jar`
into the package's `./inst/java/` folder with all its java dependencies. 

After Java compilation, the R packages has to be (re-)build and (re-)installed 
(with most likely re-starting the R session frist (Ctrl-Shift-F10 in Rstudio)). 

If developing Java in VScode - as I did here - pressing Ctr-Shift-B should allow 
to select the two most important tasks: resolving dependencies 
and compiling the Java code and distributing it 
to the right places as described above. 




